A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}

### 2022-01-12 ICLP Paper/samplepaper.tex
adjusted paper style

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\usepackage{adjustbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex,breaklines=false}
\usepackage{multirow}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{A decomposition Approach for solving the JSP using multi-shot ASP\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    Scheduling plays a significant role in the success of any manufacturing system where the tasks are assigned to a limited number of resources to be scheduled. Job-shop Scheduling Problem (JSP) is one of the most challenging problems in production systems. JSP deals with assigning the tasks to a set of machines and determining the sequence of the tasks on each machine while completing them as early as possible. This paper applied a decomposition approach that splits the problem into a pre-defined set of small problems called Time Windows (TWs) and solves each separately in sequential order. Our proposed model is split into two main phases for solving the (JSP). The decomposition phase assigns each operation to a particular TW while satisfying the precedence constraint. The second phase is the scheduling phase, in which the model starts to optimize the first TW and continues until finishing the last TW. We built our model using Answer Set Programming (ASP). A Multi-shot solving paradigm is used to deal with the decomposition approach and differenc logic to handle the constraints. To evaluate the proposed work, we tested our model on a set of benchmark instances with different sizes and the results showed that the multi-shot solving is better than the single-shot when the number of operations increases. 
\keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{splncs04}
\bibliography{Ref}

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass{tlp} % \documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet,times,courier}
\usepackage{listings}
\usepackage[inline]{enumitem}
\usepackage{adjustbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\lstset{numberbychapter=false,numbers=left,numberblanklines=false,basicstyle=\footnotesize\ttfamily,xleftmargin=5ex,breaklines=false}
\usepackage{multirow}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}

\lefttitle{Mohammed M.\ S.\ El-Kholany, Martin Gebser, Konstantin Schekotihin}

\jnlPage{1}{8}
\jnlDoiYr{2021}
\doival{10.1017/xxxxx}
%
\title{A decomposition Approach for solving the JSP using multi-shot ASP%
% \thanks{This work was partially funded by
% KWF project 28472,
% cms electronics GmbH,
% FunderMax GmbH,
% Hirsch Armbänder GmbH,
% incubed IT GmbH,
% Infineon Technologies Austria AG,
% Isovolta AG,
% Kostwein Holding GmbH, and
% Privatstiftung Kärntner Sparkasse.}%
}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
% \author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-0002-1088-2081} \and
% Martin Gebser\inst{1,2}\orcidID{0000-0002-8010-4752} \and
% Konstantin Schekotihin\inst{1}\orcidID{0000-0002-0286-0958}}
% %
% \authorrunning{M. El-Kholany et al.}
% % First names are abbreviated in the running head.
% % If there are more than two authors, 'et al.' is used.
% %
% \institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
% \email{\{mohammed.el-kholany, martin.gebser and konstantin.schekotihin\}@aau.at}\\
% %\url{http://www.springer.com/gp/computer-science/lncs} \and
% Technische Universität Graz, Graz, Austria\\
% \email{mgebser@ist.tugraz.at}}
\begin{authgrp}
\author{\sn{Mohammed M.\ S.} \gn{El-Kholany}} % \inst{1}\orcidID{0000-0002-1088-2081} \and
\affiliation{University of Klagenfurt, Austria \and Cairo University, Egypt}
\author{\sn{Martin} \gn{Gebser}} % \inst{1,2}\orcidID{0000-0002-8010-4752} \and
\affiliation{University of Klagenfurt, Austria \and Graz University of Technology, Austria}
\author{\sn{Konstantin} \gn{Schekotihin}} % \inst{1}\orcidID{0000-0002-0286-0958}
\affiliation{University of Klagenfurt, Austria}
\end{authgrp}

\history{\sub{xx xx xxxx;} \rev{xx xx xxxx;} \acc{xx xx xxxx}}

\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    Scheduling plays a significant role in the success of any manufacturing system where the tasks are assigned to a limited number of resources to be scheduled. Job-shop Scheduling Problem (JSP) is one of the most challenging problems in production systems. JSP deals with assigning the tasks to a set of machines and determining the sequence of the tasks on each machine while completing them as early as possible. This paper applied a decomposition approach that splits the problem into a pre-defined set of small problems called Time Windows (TWs) and solves each separately in sequential order. Our proposed model is split into two main phases for solving the (JSP). The decomposition phase assigns each operation to a particular TW while satisfying the precedence constraint. The second phase is the scheduling phase, in which the model starts to optimize the first TW and continues until finishing the last TW. We built our model using Answer Set Programming (ASP). A Multi-shot solving paradigm is used to deal with the decomposition approach and differenc logic to handle the constraints. To evaluate the proposed work, we tested our model on a set of benchmark instances with different sizes and the results showed that the multi-shot solving is better than the single-shot when the number of operations increases. 
% \keywords{Job-shop Scheduling Problem  \and Answer Set Programming \and Decomposition.}
\end{abstract}
%
\begin{keywords}
Job-shop Scheduling Problem, Answer Set Programming, Decomposition
\end{keywords}
%
%
\section{Introduction}
In today's competitive markets, manufacturers have to respond quickly to orders and meet shipping dates committed to the customers. This requires the ability to schedule production activities to use the available scarce resources efficiently. Effective scheduling techniques are essential in complex manufacturing systems such as semiconductor manufacturing. In general, scheduling operations is one of the most critical issues in the planning and managing of the manufacturing processes\cite{uzsoy2000performance}.

@@

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\bibliographystyle{tlplike} % \bibliographystyle{splncs04}
\bibliography{Ref}
